LaMachine: A meta-distribution for NLP software

### 2018-07-26 docs/lamachine_extabstract_clarin2018.tex
right stylesheet for CLARIN2018 paper
[paper] minor edits/fixes after iris' edits

\documentclass[a4paper,11pt]{article}
%\usepackage{CLARIN2018}
% - - - - - - - IMPORTANT - - - - - - - -
% The next three lines allow XeLaTeX, graphics import and hyperlinks, set font and language
%\usepackage{xltxtra,polyglossia,graphicx,hyperref}
%\setmainfont[Mapping=tex-text]{Times}
%\setdefaultlanguage{english}
% If for some reason the above three lines are not compatible with your LaTeX installation,
% comment out the above three instructions and uncomment the following four instead:
\usepackage{times}
\usepackage{hyperref}
\usepackage{graphicx}
%\usepackage{latexsym}
\usepackage[english]{babel}

@@

Software is a key deliverable and a vital component for research in projects such as those under the CLARIN umbrella. It
is software that provides researchers the instruments to yield for their research;
% without it a lot of research wouldbecome highly unfeasible or right-out impossible. 
It is CLARIN's core mission to make digital language resources,
including software, available to the wider research community.

@@

We participated the ZonMw project entitled ``Tekstmining in het toezicht: een exploratieve studie naar de automatische verwerking van klachten ingediend bij het Landelijk Meldpunt Zorg"\footnote{project website: \url{https://www.zonmw.nl/nl/onderzoek-resultaten/kwaliteit-van-zorg/programmas/project-detail/effectief-toezicht/tekstmining-in-het-toezicht-een-exploratieve-studie-naar-de-automatische-verwerking-van-klachten-in/}. } led by IQhealthcare\footnote{\url{http://www.iqhealthcare.nl/nl/}}, the scientific center for healthcare quality of RadboudUMC.
This project took place at the Dutch Health Inspectorate and aimed to apply text mining techniques to health care complaints that have been registered at the national contact point for health care (Landelijk Meldpunt Zorg \url{https://www.landelijkmeldpuntzorg.nl})
We investigated the usefulness of text mining to categorise and cluster complaints, to automatically determine the severity of incoming complaints, to extract patterns  and to identify risk cases. This project turned out to be a good test case of the applicability and usefulness of the LaMachine software as a standalone research environment.
As the complaint data is highly sensitive, this data could not leave the secure servers from the health inspectorate and was stored an environment without internet acces. We needed to bring the software to the data via a shared folder.

We created a pre-compiled virtual image of LaMachine\footnote{ Installation of LaMachine begins with a single bootstrap command, see
\url{https://proycon.github.io/LaMachine}} and succeeded in running it as a 64-bits Arch Linux-based VM inside another VM with Windows 2012 in which we did have administrative rights but no internet acces. In terms of hardware we ran on a machine with 8 cores and  32gb internal memory available.
%using VirtualBox and Vagrnt on the Windows VM
Lamachine provided a fully functional research environment and we ran all our experiments within LaMachine. We interacted with LaMachine both through the command line, which offers a standard
shell and enables access to all lower-level tools and programming languages; or through the (offline) webbrowser to apply the Jupyter Notebook environment\footnote{\url{https://jupyter.org/}}, which offers a more graphical scripting environment
for e.g. Python and R that has gained great popularity in the scientific community.

LaMachine comes with some simple data sharing facilities that allowed us to acces the sensitive complaint data via a  single shared dataspace between host and the VM. (Note that extensive data search and management functions are deliberately beyond the scope of LaMachine, and left to more high-level tooling.)

@@

The recent release of LaMachine v2, which constituted a full rewrite, has opened up LaMachine to outside
contribution. Contributor documentation has been written, and at this stage, we greatly welcome external participants
to join in. Use cases as the example in section \ref{sec-case} contributing to thorough testing and running of LaMachine in less ideal circumstances such as nested VM constructions and offline usage.

@@

\section*{Acknowlegdement}

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage{CLARIN2018}
% - - - - - - - IMPORTANT - - - - - - - -
% The next three lines allow XeLaTeX, graphics import and hyperlinks, set font and language
%\usepackage{xltxtra,polyglossia,graphicx,hyperref}
%\setmainfont[Mapping=tex-text]{Times}
%\setdefaultlanguage{english}
% If for some reason the above three lines are not compatible with your LaTeX installation,
% comment out the above three instructions and uncomment the following four instead:
\usepackage{times}
\usepackage{hyperref}
\usepackage{graphicx}
%\usepackage{latexsym}
\usepackage[english]{babel}

@@

Software is a key deliverable and a vital component for research in projects such as those under the CLARIN umbrella. It
is software that provides researchers the instruments to yield for their research;
% without it a lot of research would become highly unfeasible or right-out impossible.
It is CLARIN's core mission to make digital language resources,
including software, available to the wider research community.

@@

We participated in the dutch ZonMw project entitled ``Tekstmining in het toezicht: een exploratieve studie naar de
automatische verwerking van klachten ingediend bij het Landelijk Meldpunt Zorg"\footnote{project website:
\url{https://www.zonmw.nl/nl/onderzoek-resultaten/kwaliteit-van-zorg/programmas/project-detail/effectief-toezicht/tekstmining-in-het-toezicht-een-exploratieve-studie-naar-de-automatische-verwerking-van-klachten-in/}.
} led by IQhealthcare\footnote{\url{http://www.iqhealthcare.nl/nl/}}, the scientific centre for healthcare quality of RadboudUMC.
This project took place at the Dutch Health Inspectorate and aimed to apply text mining techniques to health care complaints that have been registered at the national contact point for health care (Landelijk Meldpunt Zorg \url{https://www.landelijkmeldpuntzorg.nl})
We investigated the usefulness of text mining to categorise and cluster complaints, to automatically determine the
severity of incoming complaints, to extract patterns  and to identify risk cases. This project turned out to be a good
test case of the applicability and usefulness of LaMachine as a standalone research environment.
As the complaint data is highly sensitive, it could not leave the secure servers from the health inspectorate and was
stored an environment without internet access. We needed to bring the software to the data via a shared folder.

We used a virtual machine (VM) image of LaMachine\footnote{Installation of LaMachine begins with a single bootstrap command, see
\url{https://proycon.github.io/LaMachine}} and succeeded in running it as a 64-bits Linux-based VM inside another
VM with Windows 2012 in which we did have administrative rights but no internet access, i.e. the VM that was offered to
us for this project. In terms of hardware we ran on a
machine with 8 cores and  32GB internal memory available.
%using VirtualBox and Vagrnt on the Windows VM
Lamachine provided a fully functional research environment and we ran all our experiments within LaMachine. We interacted with LaMachine both through the command line, which offers a standard
shell and enables access to all lower-level tools and programming languages; or through the (offline) webbrowser to use the Jupyter Notebook environment\footnote{\url{https://jupyter.org/}}, which offers a more graphical scripting environment
for e.g. Python and R that has gained great popularity in the scientific community.

LaMachine comes with some simple data sharing facilities that allowed us to access the sensitive complaint data via a single shared dataspace between host and the VM. (Note that extensive data search and management functions are deliberately beyond the scope of LaMachine, and left to more high-level tooling.)

@@

The recent release of LaMachine v2, which constituted a full rewrite, has opened up LaMachine to outside
contribution. Contributor documentation has been written, and at this stage, we greatly welcome external participants
to join in. Use cases as the example in section \ref{sec-case} contribute to thorough testing and running of LaMachine in less ideal circumstances such as nested VM constructions and offline usage.

@@

\section*{Acknowledgement}
